Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Adde prop density vs a1 plot to Figure 9 (d)

@@

  bin_obj <- calc_bins_y(bin1 = xbins, r2 = r2, q = 0.1)

  bin2 <- bin_obj$bin2
  a1 <- bin_obj$a1

@@

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve,
    df_bin = df_bin_scurve,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(bin1 = xbins,
           bin2 = bin2,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve),
           a1 = round(a1, 2))

@@

## Find the minimum MSE when have duplicate a1
error_scurve <- error_scurve |>
  group_by(a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()

@@

@@

@@

mse_scurve_b + a1_m_scurve +
  mse_scurve_lwd + 
  plot_layout(ncol=2)
```

>>>>

```{r}
#| label: solve-quad-fun

quad <- function(a = 3, b = 2 * a2, c = -(a2^2 + a1^2))
{
  a <- as.complex(a)
  answer <- c((-b + sqrt(b^2 - 4 * a * c)) / (2 * a),
              (-b - sqrt(b^2 - 4 * a * c)) / (2 * a))
  if(all(Im(answer) == 0)) answer <- Re(answer)
  if(answer[1] == answer[2]) return(answer[1])
  answer[answer>0] ## only positive 
}

@@

  bin_obj <- calc_bins_y(
    bin1 = xbins, 
    r2 = r2, 
    q = 0.1)

  bin2 <- bin_obj$bin2
  a1 <- bin_obj$a1
  a2 <- bin_obj$a2

@@

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve,
    df_bin = df_bin_scurve,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(bin1 = xbins,
           bin2 = bin2,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve),
           a1 = round(a1, 2),
           a2 = round(a2, 2),
           side_length = quad(a=3, b = 2 * a2, c = -(a2^2 + a1^2)))

@@

## Find the minimum MSE when have duplicate a1
error_scurve <- error_scurve |>
  group_by(a1) |>
  filter(MSE == min(MSE)) |>
  ungroup() |>
  mutate(prop_dens = b_non_empty/side_length)

base_line_prop_dens <- error_scurve |>
  filter(a1 == min(a1)) |>
  pull(prop_dens)

error_scurve <- error_scurve |>
  mutate(prop_comp = prop_dens/base_line_prop_dens)

@@

prop_dens_a1 <- ggplot(error_scurve,
                     aes(x = a1,
                         y = prop_comp)) +
  geom_vline(xintercept = 0.12, linetype="solid",
             color = "#006d2c", linewidth=1) +
  geom_vline(xintercept = 0.10, linetype=2,
             color = "#54278f", linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#08519c", linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = paste("proportion of densities")) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

<!--base line -->

@@

mse_scurve_b + a1_m_scurve +
  mse_scurve_lwd + prop_dens_a1 +
  plot_layout(ncol=2)
```
